---
title: "Initial Korean covid 19"
author: "Lele Nicholson"
date: "October 21st, 2025"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Your Question - Is dying independent of sex?






## Graphical results - use ggplot commands to do this  

```{r}
dd2 <- kRdata %>% group_by(result,Sex) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=result,y=count,fill=Sex))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=result,y=prcnt*100,fill=Sex)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```

After analyzing, I realized that the percentage of living people are higher than the percentage ofe the dead ones. Also looking in the chart I found out that 2/3 of the dead people were men by 63%, while 1/3 were women by 37%. Suggesting that it was killing the men more than it did the women, while the chart of living people had 57% of living women and 43% of living men.



  
## Numerical results

```{r}
table1 <- xtabs(~result + Sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```

## Inferential results 

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

While analyzing the Inferential results, I found out the men dying in Korea from COVID by 2.3 percent than the women. This Proof also aligns with the charts from before. The p-value is low,meaning the man has more chance of getting COVID then the women.

## Conclusions

While doing this assignment, I used the categorical-categorical helper file to get the Covid data in Korea. The data gathered was Graphical, Numerical, Inferential results. i was able to find out that the men her 2/3 dying more than the women due to COVID, While the women are 1/3. The men were about 64% dead while the women 36% dead and the living men is 53%, while the women are 44%.